Leaf traits drive differences in biomass partitioning among major plant functional types

### 2014-12-16 manuscript.Rnw
caption and labels update figure 4

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure4.pdf}
    \caption{Modest effects of climate on three size-invariant variables, compared to the very large effect of plant functional type on mass-based variables ($M_F/A_S$), and convergence in area-based variables ($A_F/A_S$). Solid lines are generalized additive model (GAM) fits (with a base dimension of 3, larger values resulted in biologically implausible relationships). Grey areas are approximate 95\% confidence intervals, calculated by the GAM after averaging each variable by species/dataset combination.}
  \label{fig:figure4}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure4.pdf}
    \caption{Modest effects of climate on leaf mass and area per unit stem basal area, compared to the very large effect of plant functional type on mass-based variables ($M_F/A_S$). Solid lines are generalized additive model (GAM) fits (with a base dimension of 3, larger values resulted in biologically implausible relationships). Grey areas are approximate 95\% confidence intervals, calculated by the GAM. To account for within-species and contributed dataset correlations, data were first averaged by species/dataset combination.}
  \label{fig:figure4}
\end{figure}
